Rank Verification for Exponential Families

### 2017-06-28 verifying-winner.tex
finishing touches

We now state our main theorem: under a mild technical assumption, Procedures 1--3 described above are statistically valid, even accounting for the selection.
\begin{theorem}
\label{thm:main}
Assume the model~\eqref{eq:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Then:
\begin{enumerate}
\item Procedure 1 has exact level $\alpha$ conditional on $H$ being true (conditional on the best population not winning), and marginally has level $\alpha\PP(H \text{ is true}) \leq \alpha \left(1-\frac{1}{n}\right)$.
\item Procedure 2 gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
\item Procedure 3 is a conservative stepwise procedure with FWER no larger than $\alpha$.
\end{enumerate}
\end{theorem}

Note that Theorem~\ref{thm:main} implies that we could actually replace $\alpha$ with $\alpha \frac{n}{n-1}$ to obtain a more powerful version of Procedure 1 when $n$ is not too large.

@@

\subsection{Related work}\label{sec:related}

>>>>

We now state our main theorem: under a mild technical assumption, Procedures 1--3 described above are statistically valid, even accounting for the selection.
\begin{theorem}
\label{thm:main}
Assume the model~\eqref{eq:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Then:
\begin{enumerate}
\item Procedure 1 has exact level $\alpha$ conditional on $H$ being true (conditional on the best population not winning), and marginally has level $\alpha \cdot \PP(H \text{ is true}) \leq \alpha \left(1-\frac{1}{n}\right)$.
\item Procedure 2 gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
\item Procedure 3 is a conservative stepwise procedure with FWER no larger than $\alpha$.
\end{enumerate}
\end{theorem}

Note that Theorem~\ref{thm:main} implies that we could actually replace $\alpha$ with $\frac{n}{n-1} \alpha$ to obtain a more powerful version of Procedure 1 when $n$ is not too large.

@@

\subsection{Related work}
\label{sec:related}
